Duration Analysis for Performing-Articulation performances

### 2020-05-19 material/analysis/expression/stim_a/ioi_duration.Rmd
add comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of performing performance from teaching-v2.0 (duration).

@@

### Sequence plot
- Right wrap: Subject Number

@@

### Distribution plot
#### Legato
```{r duration_dis_leg, fig.width = 12, echo = FALSE}
p_duration_dis_leg <- ggplot(dt_duration[Subcomponent == "Legato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Legato)")
p_duration_dis_leg
```

>>>>

Description: This is a rough overview of performing performance (duration) from teaching-v2.0.

@@

#### Sequence plot
- Right wrap: Subject Number

@@

#### Distribution plot
- Right wrap: Trial Number
- Upper wrap: Subject Number

#### Legato
```{r duration_dis_leg, fig.width = 12, echo = FALSE}
p_duration_dis_leg <- ggplot(dt_duration[Subcomponent == "Legato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Legato)")
p_duration_dis_leg
```
